\documentclass[12pt,letterpaper,twosided]{report}
\usepackage{afterpage}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{alltt}
\usepackage{amsmath}
\usepackage{amssymb,amsthm,amsfonts}
\usepackage{array}
\usepackage[english]{babel}
\usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[bookmarks=true, pdftitle={Novel Spectral Representations and Sparsity-Driven Algorithms for Shape Modeling and Analysis}, pdfauthor={Ming Zhong}]{hyperref}
\usepackage{lingmacros}
\usepackage{multirow}
\usepackage{pb-diagram}
\usepackage{pbox}
\usepackage{ragged2e}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{tabularx}
\usepackage{times}
\usepackage{tree-dvips}
\usepackage{url}
\usepackage{xcolor}
\usepackage{cuted}

\allowdisplaybreaks

\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{definition}[theorem]{Definition}
\newtheorem{problem}[theorem]{Problem}
\newtheorem{corollary}{Corollary}[section]

\DeclareMathOperator*{\HK}{HK}
\DeclareMathOperator*{\HKS}{HKS}
\DeclareMathOperator*{\WKS}{WKS}
\DeclareMathOperator*{\KS}{KS}
\DeclareMathOperator*{\HKC}{HKC}
\DeclareMathOperator*{\GPS}{GPS}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\dvol}{dvol}

\begin{document}
\pagenumbering{gobble}
\title{\bf{Novel Spectral Representations and
Sparsity-Driven Algorithms for Shape Modeling and Analysis}}

\vspace*{3\baselineskip}
\begin{center}
{\bf\Large Novel Spectral Representations and
Sparsity-Driven Algorithms for Shape Modeling and Analysis}
\end{center}
\vspace*{3\baselineskip}
\centerline{A Dissertation presented}
\vspace*{1\baselineskip}
\centerline{by}
\vspace*{1\baselineskip}
\centerline{\bf{Ming Zhong}}
\vspace*{1\baselineskip}
\centerline{to}
\vspace*{1\baselineskip}
\centerline{The Graduate School}
\vspace*{1\baselineskip}
\centerline{in Partial Fulfillment of the}
\vspace*{1\baselineskip}
\centerline{Requirements}
\vspace*{1\baselineskip}
\centerline{for the Degree of}
\vspace*{1\baselineskip}
\centerline{\bf{Doctor of Philosophy}}
\vspace*{1\baselineskip}
\centerline{in}
\vspace*{1\baselineskip}
\centerline{\bf{Computer Science}}
\vspace*{2\baselineskip}
\centerline{Stony Brook University}
\vspace*{2\baselineskip}
\centerline{\bf{Spring 2016}}

\newpage
\pagenumbering{gobble}

\vspace*{32\baselineskip}
\centerline{Copyright by}
\centerline{\bf{Ming Zhong}}
\centerline{\bf{2016}}

\newpage
\pagenumbering{roman}
\setcounter{page}{2}

\centerline{\bf{Stony Brook University}}
\vspace*{1\baselineskip}
\centerline{The Graduate School}
\vspace*{2\baselineskip}
\centerline{\bf{Ming Zhong}}
\vspace*{2\baselineskip}
\centerline{We, the dissertation committee for the above candidate for the}
\vspace*{1\baselineskip}
\centerline{Doctor of Philosophy degree, hereby recommend}
\vspace*{1\baselineskip}
\centerline{acceptance of this dissertation}
\vspace*{2\baselineskip}
\centerline{\bf{Hong Qin - Dissertation Advisor}}
\centerline{\bf{Professor, Department of Computer Science}}
\vspace*{2\baselineskip}
\centerline{\bf{Joseph Mitchell - Chairperson of Defense}}
\centerline{\bf{Professor, Department of Applied Mathematics and Statistics}}
\vspace*{2\baselineskip}
\centerline{\bf{Xianfeng David Gu}}
\centerline{\bf{Associate Professor, Department of Computer Science}}
\vspace*{2\baselineskip}
\centerline{\bf{Xin Li}}
\centerline{\bf{Associate Professor, School of Electrical Engineering \& Computer Science}}
\centerline{\bf{Louisiana State University}}
\vspace*{2\baselineskip}
\centerline{This dissertation is accepted by the Graduate School}
\vspace*{3\baselineskip}
\centerline{Charles Taber}
\centerline{Dean of the Graduate School}

\afterpage{\null\newpage}

\centerline{Abstract of the Dissertation}
\vspace*{1\baselineskip}
\centerline{\bf{Novel Spectral Representations and Sparsity-Driven
Algorithms for Shape Modeling and Analysis}}
\vspace*{1\baselineskip}
\centerline{by}
\vspace*{1\baselineskip}
\centerline{\bf{Ming Zhong}}
\vspace*{1\baselineskip}
\centerline{\bf{Doctor of Philosophy}}
\vspace*{1\baselineskip}
\centerline{in}
\vspace*{1\baselineskip}
\centerline{\bf{Computer Science}}
\vspace*{1\baselineskip}
\centerline{Stony Brook University}
\vspace*{1\baselineskip}
\centerline{\bf{2016}}
\vspace*{2\baselineskip}

In this dissertation, we focus on extending spectral methods for shape analysis 
and processing by incorporating spectral graph wavelets and sparsity-seeking
algorithms. Spectral graph wavelets (SGWs) are defined with the eigenfunctions of
graph Laplacian, with scaling implemented in the spectral domain. Comparing with
the Laplacian eigenbasis, the SGWs are localized in both space and frequency domains, 
and thus are more suitable for representing local geometry. In recent years, sparsity has
become an important concept in signal processing. By supplying a
rich, often redundant, dictionary of elementary vectors and forcing certain
sparsity constraints, real life signals can often be approximated by very concise 
coefficient representations with great fidelity, or can be well reconstructed 
from imprecise or incomplete observations. Inspired by its many successful applications in 
computer vision and image processing, we aim to employ sparse modeling techniques to 
solve various shape modeling problems. 

Conventional spectral mesh compression employs the eigenfunctions of mesh
Laplacian as shape bases, which are highly inefficient in representing local
geometry. To ameliorate, we advocate an innovative approach to 3D mesh
compression using spectral graph wavelets as dictionary to encode mesh geometry.
The spectral graph wavelets are locally defined at individual vertices and can
better capture local shape information than Laplacian eigenbasis. The 
multi-scale SGWs form a redundant dictionary as shape basis, so we formulate 
the compression of 3D shape as a sparse approximation problem that can be 
readily handled by greedy pursuit algorithms.

Surface inpainting refers to the completion or recovery of missing shape
geometry based on the shape information that is currently available. We
devise a new surface inpainting algorithm founded upon the theory and
techniques of sparse signal recovery. Instead of estimating the missing
geometry directly, our novel method is to find this low-dimensional
representation which describes the entire original shape. More specifically,
we find that, for many shapes, the vertex coordinate function can be well
approximated by a very sparse coefficient representation with respect to the
dictionary comprising its Laplacian eigenbasis, and it is then possible to
recover this sparse representation from partial measurements of the original
shape. Taking advantage of the sparsity cue, we advocate a novel variational
approach for surface inpainting, integrating data fidelity constraints on the
shape domain with coefficient sparsity constraints on the transformed domain.
Because of the powerful properties of Laplacian eigenbasis, the inpainting
results of our method tend to be globally coherent with the remaining shape.

Informative and discriminative feature descriptors are vital in qualitative and
quantitative shape analysis for a large variety of graphics applications. We
advocate novel strategies to define generalized, user-specified features on
shapes. Our new region descriptors are primarily built upon the coefficients of
spectral graph wavelets that are both multi-scale and multi-level in nature,
consisting of both local and global information. Based on our novel spectral
feature descriptor, we developed a user-specified feature
detection framework and a tensor-based shape matching algorithm.

Through various experiments, we demonstrate the competitive performance of our
proposed methods and the great potential of redundant spectral basis and
sparsity-driven methods for shape modeling. We conclude this dissertation by
discussing some remaining challenges and new research directions.

%%%%%%%%%%%%%%%%%%%%%%%%%% end of abstract %%%%%%%%%%%%%%%%%%%%%%%%%%

\onehalfspacing

\tableofcontents

\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{\listfigurename}
\listoffigures

%\clearpage
%\phantomsection
%\addcontentsline{toc}{chapter}{\listtablename}
%\listoftables

%\centerline{\bf{Acknowledgements}}
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

First of all, I would like to thank my advisor, Professor Hong Qin, for his
persistent support and guidance throughout my PhD study. Without his
inspirations and encouragement this dissertation would not be possible. 
I feel enormously fortunate to have the opportunity to work with him. 

I am deeply grateful to all my committee members. Professor Joseph Mitchell
and Professor Xianfeng Gu also served in my thesis proposal committee. And I
would like to thank Professor Xiangming Jiao and Professor Alex Berg for serving in
my research proficiency exam. Specially, I would thank Professor Xin Li for taking 
the time to serve as the external examiner of my defense committee. 

I would like to thank my research collaborators including Dr. Tingbo Hou, Dr. Shengfa Wang, 
Xiaohua Hou and Nannan Li. I feel privileged to work with these wonderful colleagues
and I am indebted to their help and insights. 

Many of my other colleagues at Stony Brook and the two companies where I did internship,
DreamWorks Animation and Google, also offered me very helpful suggestions and advices. 
In particular, I want to express my gratitude to Dr. Rui Shi, 
Dr. Deepak Tolani, Dr. Jianping Hu, Dr. Xiaochao Wang, Ning Zhang and Dr. Vitalii Li. 

Last but not least, I would like to give my special thanks to my parents and
my wife. Without their support and encouragement, I would never have had this long
but rewarding journey. 
\\
\begin{flushright}
Ming Zhong\hspace*{0.25in}
\end{flushright}


\newpage
\chapter*{Publications}
\addcontentsline{toc}{chapter}{Publications}

\begin{enumerate}
\item \textbf{Ming Zhong} and Hong Qin. ``Surface Inpainting with Sparsity Constraints.'' \emph{Computer Aided Geometric Design}, 41:23-35, 2016
\item Nannan Li, Shengfa Wang, \textbf{Ming Zhong}, Zhixun Su, and Hong Qin. ``Generalized Local-to-global Shape Feature Detection based on Graph Wavelets.'' \emph{IEEE Transaction on Visualization and Computer Graphics}, 2015
\item \textbf{Ming Zhong} and Hong Qin. ``Sparse approximation of 3D shapes via spectral graph wavelets.'' \emph{The Visual Computer}, 30(6-8): 751-761, 2014.
\item \textbf{Ming Zhong}. ``Harmonic Shape Analysis: From Fourier to Wavelets.'' \emph{Technical Report, Stony Brook University}, 2012.
\item Tingbo Hou, Xiaohua Hou, \textbf{Ming Zhong}, and Hong Qin. ``Bag-of-feature-graphs: A new paradigm for non-rigid shape retrieval.'' In \emph{Pattern Recognition (ICPR), 2012 21st International Conference on}, pp. 1513-1516. IEEE, 2012.
\item \textbf{Ming Zhong}, Tingbo Hou, and Hong Qin. ``A hierarchical approach to high-quality partial shape registration.'' In \emph{Pattern Recognition (ICPR), 2012 21st International Conference on}, pp. 113-116. IEEE, 2012.
\item Tingbo Hou, \textbf{Ming Zhong}, and Hong Qin. ``Diffusion-driven high-order matching of partial deformable shapes.'' In \emph{Pattern Recognition (ICPR), 2012 21st International Conference on}, pp. 137-140. IEEE, 2012.
\end{enumerate}

\newpage
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{\thepage}
\fancyhead[LO]{\leftmark}
\fancyhead[RE]{\rightmark}
\fancyfoot{}
\renewcommand{\headrulewidth}{0.5pt}
\pagenumbering{arabic}

\graphicspath{{fig-intro/}}
\include{chap-intro}
\graphicspath{{fig-background/}}
\include{chap-background}
\graphicspath{{fig-approximation/}}
\include{chap-approximation}
\graphicspath{{fig-inpainting/}}
\include{chap-inpainting}
\graphicspath{{fig-feature/}}
\include{chap-feature}
\graphicspath{{fig-matching/}}
\include{chap-matching}
\include{chap-conclusion}


\phantomsection
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{plain}
\bibliography{references}

\end{document} 